---
title: "Hesaba COVID-19 Package"
author:
- name: Mojtaba Yaghoobzadeh
abstract: " This package is part of Hesaba internship tasks. You can use this package to get up-to-date COVID-19 data, plot data on world map and plot time series."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Hesaba COVID-19 Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<br> <br> <br>

# Note

Remember to use this package, you need to import these packages:

- tidyverse
- rowrldmap

<br>

# Examples

## getData()
You can get up-to-date COVID-19 data from Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE).
This dataset contains Country, Date, Deaths, Confiremed, Recovered and Cumulative data.
```{r}

library(HesabaCovid)
library(tidyverse)
library(rworldmap)

df <- getData()
head(df)
```

## plotTimeSeries(country, dateFrom, dateTo)
plotTimeSeries can plot time series for a country between two dates.
Date must be in "YYYY-MM-DD" format.

```{r, fig.width=7}
library(HesabaCovid)
library(tidyverse)
library(rworldmap)

plotTimeSeries(country = "Iran", dateFrom = "2020-05-10",dateTo =  "2020-08-05")
```

```{r, fig.width=7}
library(HesabaCovid)
library(tidyverse)
library(rworldmap)

plotTimeSeries(country = "US",dateFrom =  "2020-05-10",dateTo = "2020-08-05")
```

## plotWorld(plotType, date)
Given a plot type and a date, plotWorld function can plot datas on world map.
Plot type can be "Deaths" or "Confiremed".
Date must be in "YYYY-MM-DD" format.
```{r, fig.width=8, fig.height=7}
library(HesabaCovid)
library(tidyverse)
library(rworldmap)

plotWorld("Confirmed", "2020-10-22")
```

```{r, fig.width=8, fig.height=7}
library(HesabaCovid)
library(tidyverse)
library(rworldmap)

plotWorld("Deaths", "2020-10-22")
```
